### 2022-01-17 manuscript/manuscript.Rmd
Update manuscript.Rmd

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
always_allow_html: true

documentclass     : "apa6"
classoption       : "man"
output            : 
  papaja::apa6_pdf:
    includes:
        after_body: "supplementary_information.tex"
---

@@

```{r render_appendix, include=FALSE}
render_appendix("supplementary_information.Rmd")
```

>>>>

floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
always_allow_html: true
appendix: "supplementary_information.Rmd"

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

@@
